\cvsection{Experience}
\begin{cventries}
%---------------------------------------------------------
\cventry
{Senior Platform Engineer} % Job title
{DoItNow!} % Organization
{Remote/Barcelona, Spain} % Location
{Mar. 2021 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{\textbf{Platform engineer} with a diverse skill set developed through projects in both HPC, Kubernetes, and cloud native technologies.}
\item{\textbf{Evaluation of storage multitenancy in AI cluster}. Evaluation of multitenancy in 4 nodes AI cluster with 32xNVIDIA B200 + DDN Lustre EXAScale solution 130TB for data isolation.}
\item{\textbf{Architected genomic analysis pipeline over Kubernetes}. Platform integration for to abstract the execution of genomic analysis pipelines (GATK Genome Sequencing variant calling) using Nextflow and Cromwell over AKS Kubernetes clusters with ARGO Workflows and Kueue.}
\item{\textbf{Led the deployment of Charmed OpenStack clusters} private clouds with ~15 nodes + distributed storage + Infiniband + NVIDIA GPUs, enabling virtualized HPC and Kubernetes clusters for multiple tenants using GPU/VF passthrough and .}
\item{\textbf{Kargo evaluation in early stage:} Evaluated Kargo CI/CD tool for staged rollouts on Kubernetes clusters.}
\item{\textbf{Evaluation of Kueue} on AWS EKS clusters, testing the resource allocation for HPC/ML/AI workloads.}
\item{\textbf{Integrated CernVM-FS (CVMFS) CSI driver into AWS EKS} giving researchers immediate access to scientific software stacks from Kubernetes pods.}
\item{\textbf{Designed and delivered an HPC cloud-bursting} solution scalable from 10 to 100s of nodes for a Synchrotron Light facility on GCP, enabling dynamic scale-out of compute resources for the HPC on-premise solution.}
\item{\textbf{Participated in the development of a hybrid workflow management PAAS}, enabling researchers to submit hybrid workflows (HPC/ML/AI) in an energy-efficient manner to on-premise and cloud HPC clusters.}
\item{\textbf{Participated in the deployment of a Spanish national supercomputer}, 256 thin nodes + 64 GPU nodes, automating provisioning and configuration with Cobbler and Saltstack.}
\item{\textbf{Supported lift-and-shift migration of HPC on-premise to AWS} (Terraform, Ansible, CI/CD, Lustre), maintaining SLAs for critical research workflows.}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Freelance DevOps Engineer} % Job title
{Freelance.} % Organization
{Remote, Spain} % Location
{2022 - 2024 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{\textbf{Debugged and optimized the main SaaS product on AWS EKS.}}
\item{Improved API response from ~60s to sub-second adding missing MongoDB indexes.}
\item{Migrated EBS volumes, tuned MongoDB, and adjusted Kubernetes pod resources.}
\item{\textbf{Implemented a big data ETL pipeline on Azure}, feeding ML models for commercial recommendations.}
\item{Integrated Azure DataFactory, PostgreSQL, and custom VPN to securely connect to AWS-based modules.}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{HPC Linux System Administrator} % Job title
{BSC-CNS - Barcelona Supercomputing Center} % Organization
{Barcelona, Spain} % Location
{Sep. 2017 - Mar 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{\textbf{Linux System administrator} at the Operations team, responsible for maintaining the IT infrastructure of the center, including general services and the supercomputing environment.}
\item{\textbf{Marenostrum 4 cluster administration} 3456 nodes, managed with xCAT, Slurm, Intel Omni-Path and GPFS (10PB), bringing support for > 1000 users.}
\item{\textbf{Nord 3 cluster administration}, managed with xCAT, LSF, Infiniband and GPFS (10PB).}
\item{\textbf{Research clusters administration} Administration of Emerging Technologies clusters (AMD, Power9) and department clusters from (10 to 30 nodes), mostly managed with xCAT + Slurm + GPFS.}
\item{\textbf{Designed a highly available DNS system (BIND),} adding security (TSIG, chroot, zone restrictions) and managing the main BSC domain.}
\item{\textbf{Deployed and migrated the organization communication platform from Jabber to RocketChat + LDAP}, improving collaboration for +500 users and departments.}
\item{\textbf{Architected and installed an oVirt/KVM virtualization cluster}, 10 nodes with dedicated GPFS, providing a more resilient service for VM infrastructure for research departments.}
\item{\textbf{Led the migration of PhylomeDB} (http://www.phylomedb.org/) service, VMs + large MariaDB DBs, tuning performance and ensuring availability for the recently migrated department.}
\item{\textbf{Integrated CI/CD practices with Ansible and Gitlab} pipelines, automating repetitive tasks in system administration.}
\item{\textbf{Optimized TSM backup system performance}, redesigning the scheduling, reducing tasks overlaps, and improving reliability of the main backup solution for the center.}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Virtualization administrator} % Job title
{Tenea Technologies} % Organization
{Barcelona, Spain} % Location
{Mar. 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{\textbf{Maintained VMware-based virtualization infrastructure}, supporting multiple departments.}
\item{Executed disaster recovery procedures for VM backup/restore.}
\item{Automated infrastructure checks and updates with PowerShell scripts.}
\item{Tested VMware vMotion performance during company-wide infrastructure integration.}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Systems Administrator} % Job title
{Hinojosa Packaging Solutions and Aqua Service Spain } % Organization
{Valencia, Spain} % Location
{May. 2016 - Feb. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{\textbf{Provided L1 support} across multiple departments.}
\item{Maintained IT systems and internal services.}
\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
