\cvsection{Skills}
\begin{cventries}
\cventry
{} % Job title
{} % Organization
{} % Location
{} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}    
    \item{\textbf{Compute Platforms \& HPC:} Large-scale Linux clusters, hybrid HPC-cloud architectures, scheduling (Slurm, LSF, Kueue), provisioning (MAAS, Cobbler, xCAT), workflow orchestration (Argo Workflows, Nextflow, Cromwell).}
    \item{\textbf{AI:} NVIDIA BCM, NVIDIA GPUs architecture, MIG, NVIDIA GPU Operator, NVIDIA Network Operator.}
    \item{\textbf{Cloud \& Platform Engineering:} AWS, GCP, Azure, OCI, OpenStack, Proxmox, KVM/QEMU, Citrix; Kubernetes (k8s, EKS, AKS), Helm, GitOps (ArgoCD, FluxCD), multi-cluster and hybrid deployments.}
    \item{\textbf{Infrastructure as Code \& Automation:} Terraform, Ansible, Packer, SaltStack, Juju/MAAS, CI/CD (GitLab CI, Bitbucket Pipelines).}
    \item{\textbf{Storage \& Data Systems:} Parallel and distributed storage (Lustre, GPFS, BeeGFS, CEPH, CVMFS), object storage (MinIO), ZFS, XFS, NFS.}
    \item{\textbf{Networking \& Performance:} HPC networking (InfiniBand, RDMA), TCP/IP, DNS, routing, VLANs, VPNs, LACP; performance tuning and system-level optimization.}
    \item{\textbf{Observability \& Reliability:} Prometheus, Grafana, Datadog, ELK, Nagios, Icinga; monitoring, alerting, and performance analysis of distributed systems.}
    \item{\textbf{Containers \& Runtime:} Kubernetes, Docker, Helm, Apptainer/Singularity, Linux tuning; containerized workloads for HPC and AI environments.}
    \item{\textbf{Programming \& Scripting:} Git, Python, Bash, PowerShell, Perl, Java; infrastructure tooling.}
    \item{\textbf{Operating Systems:} GNU/Linux (RHEL, SLES, Rocky, Ubuntu), system administration, kernel tuning, and performance optimization.}
\end{cvitems}
}
\end{cventries}
